Converting LaTeX Legacy R Journal Articles into R Markdown Articles using texor and rebib

### 2023-09-07 texor.Rmd
don't hard code date in Rmd

---
title: "Converting LaTeX Legacy R Journal Articles into R Markdown Articles using texor and rebib"
date: "2022-11-09"
abstract: >
  In 2021 the R Journal made a change of templates for article writing to R Markdown instead of LaTeX. The reasons were to encourage better reproducibility of articles using dynamic documents, enable interactivity in articles, and to make the articles more accessible for vision-impaired readers. A resulting challenge was to explore whether legacy articles might be suitably converted into HTML output. This paper describes the process to convert an R Journal article from LaTeX to HTML format via R Markdown, and the two new R packages, \CRANpkg{texor} and \CRANpkg{rebib}, that can be used to achieve the conversion.
draft: true
author:  
  # see ?rjournal_article for more information
  - name: Abhishek Ulayil
    affiliation: Institute of Actuaries of India (student)
    address:
    - Mumbai, India
    orcid: 0009-0000-6935-8690
    email: perricoq@outlook.com
  - name: Mitch O'Hara-Wild
    affiliation: Monash University
    address:
    - Melbourne, Australia
    orcid: 0000-0001-6729-7695
    email: mail@mitchelloharawild.com
  - name: Christophe Dervieux
    affiliation: Posit PBC
    address:
    - Paris, France
    orcid: 0000-0003-4474-2498
    email: christophe.dervieux@gmail.com
  - name: Heather Turner
    affiliation: University of Warwick
    address:
    - Coventry, United Kingdom
    orcid: 0000-0002-1256-3375
    email: ht@heatherturner.net
  - name: Dianne Cook
    affiliation: Monash University
    address:
    - Melbourne, Australia
    orcid: 0000-0002-3813-7155
    email: dicook@monash.edu
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: RJreferences.bib

>>>>

---
title: "Converting LaTeX Legacy R Journal Articles into R Markdown Articles using texor and rebib"
date: "`r Sys.Date()`"
abstract: >
  In 2021 the R Journal made a change of templates for article writing to R Markdown instead of LaTeX. The reasons were to encourage better reproducibility of articles using dynamic documents, enable interactivity in articles, and to make the articles more accessible for vision-impaired readers. A resulting challenge was to explore whether legacy articles might be suitably converted into HTML output. This paper describes the process to convert an R Journal article from LaTeX to HTML format via R Markdown, and the two new R packages, \CRANpkg{texor} and \CRANpkg{rebib}, that can be used to achieve the conversion.
draft: true
author:  
  # see ?rjournal_article for more information
  - name: Abhishek Ulayil
    affiliation: Institute of Actuaries of India (student)
    address:
    - Mumbai, India
    orcid: 0009-0000-6935-8690
    email: perricoq@outlook.com
  - name: Mitch O'Hara-Wild
    affiliation: Monash University
    address:
    - Melbourne, Australia
    orcid: 0000-0001-6729-7695
    email: mail@mitchelloharawild.com
  - name: Christophe Dervieux
    affiliation: Posit PBC
    address:
    - Paris, France
    orcid: 0000-0003-4474-2498
    email: christophe.dervieux@gmail.com
  - name: Heather Turner
    affiliation: University of Warwick
    address:
    - Coventry, United Kingdom
    orcid: 0000-0002-1256-3375
    email: ht@heatherturner.net
  - name: Dianne Cook
    affiliation: Monash University
    address:
    - Melbourne, Australia
    orcid: 0000-0002-3813-7155
    email: dicook@monash.edu
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: RJreferences.bib
